---
title: "Figures"
output: html_document
---
<style type="text/css">
  .title {
    display: none;
  }
    
</style>
---


```{r, echo = FALSE}
# knitr::opts_chunk$set(echo = TRUE)
# 
# library(ggplot2)
# library(sf)
# library(readr)
# library(plotly)
# library(rnaturalearth)
# 
# world <- ne_countries(scale = "medium", returnclass = "sf") # get map
# ATLAS_space_Databank_locations <- read_csv("../../ATLAS Data/ATLAS_space_Databank_locations.csv")
# 
# map <- ggplot(data = world) +
#   geom_sf(color = "grey70", alpha = 0.4) +
#   geom_point(data = ATLAS_space_Databank_locations, aes(x = lon, y = lat), alpha = 0.8, color = 'black') +
#   geom_point(data = ATLAS_space_Databank_locations, aes(x = lon, y = lat), alpha = 1, color = 'black', fill = NA) +
#   coord_sf(expand = 0) +
#   scale_x_continuous(name = NULL, limits = c(-180, 180)) +
#   scale_y_continuous(name = NULL, limits = c(-60, 90)) +
#   theme_bw() +
#   theme(plot.title = element_text(hjust = 0.5),
#         panel.grid.major = element_blank(),
#         legend.position = "bottom",
#         strip.text = element_text(size = 20))
# 
# plotly_map <- ggplotly(map)
# 
# plotly_map
# ```

# 
```

```{r, echo = FALSE}
# knitr::opts_chunk$set(echo = TRUE)
# library(ggplot2)
# library(sf)
# library(readr)
# library(plotly)
# library(rnaturalearth)
# 
# world <- ne_countries(scale = "medium", returnclass = "sf") # get map
# ATLAS_space_geo <- read_csv("../../ATLAS Data/ATLAS_space_geo.csv")
# 
# space.location.plot <- ggplot(data = world) +
#   geom_sf(color="grey70",
#           size=1,
#           # aes(fill=rev(economy)),
#           alpha=0.4, show.legend = FALSE) +
#   geom_point(data=subset(ATLAS_space_geo),
#              aes(x=lon, y=lat,
#                  # shape=LateralDirection,
#                  fill=Language,
#                  size=StudySampleSize), # decide whether to fill in circle
#              shape=21,
#              color="black",
#              alpha=.5) +
#   geom_point(data=subset(ATLAS_space_geo),
#              aes(x=lon, y=lat), # decide whether to fill in circle
#              # shape=21,
#              fill="black",
#              size=.5,
#              alpha=.5) +
#   coord_sf(expand=0,label_graticule = "") +
#   #facet_wrap(~Domain_label, ncol=1) +
#   scale_x_continuous(name = "", limits = c(-180, 180), breaks = NULL) +
#   scale_y_continuous(name = "", limits = c(-60, 90), breaks = NULL) +
#   # scale_shape_manual(NULL, values=c(21,24), ) +
#   scale_size("Language",
#              # guide=F,
#              breaks=c(5, 50, 500),
#              range=c(.1,12)) +
#   # scale_color_discrete(NULL, guide=F) +
#   scale_fill_discrete(NULL,
#                       guide=F
#   ) +
#   # facet_wrap(~Domain, nrow = 3) +
#   theme_bw(base_size = 20) +
#   theme(plot.title = element_text(hjust=.5),
#         panel.grid.major = element_blank(),
#         axis.ticks = element_blank(),
#         legend.position='bottom',
#         legend.text = element_text(size = 12),
#         strip.text = element_text(size=20))
# space.location.plot <- ggplotly(space.location.plot)
# space.location.plot
# 
# htmlwidgets::saveWidget(space.location.plot, "space.location.plot.html", selfcontained = TRUE)

```

```{r, echo = FALSE}
# library(dplyr)
# library(plotly)
# 
# data <- read.csv("../../ATLAS Data/ATLAS_space_Databank_locations.csv")
# 
# # Create an interactive histogram broken down by continent
# plotly_hist <- function(data) {
#   # Aggregate data by continent
#   continent_counts <- data %>%
#     group_by(continent) %>%
#     summarise(count = n())
# 
# plot <- plot_ly(data = continent_counts, x = ~continent, y = ~count, type = "bar") %>%
#   layout(xaxis = list(title = "Continent"),
#          yaxis = list(title = "Count"))
# 
#   return(plot)
# }
# 
# continent_hist <- plotly_hist(data)
# 
# htmlwidgets::saveWidget(continent_hist, "continent_hist.html", selfcontained = TRUE)

```

```{r, echo = FALSE}
# knitr::opts_chunk$set(echo = TRUE)
# library(dplyr)
# library(plotly)
# 
# data <- read.csv("../../ATLAS Data/ATLAS_space_geo.csv")
# 
# plotly_hist <- function(data) {
#   FoR_counts <- data %>%
#     group_by(Preferred_FoR) %>%
#     summarise(count = n())
# 
#   plot <- plot_ly(data = FoR_counts, x = ~Preferred_FoR, y = ~count, type = "bar") %>%
#     layout(xaxis = list(title = "Preferred FoR"),
#            yaxis = list(title = "Numer of Groups Sampled"))
# 
#   return(plot)
# }
# 
# FoR_hist <- plotly_hist(data)
# 
# htmlwidgets::saveWidget(FoR_hist, "FoR_hist.html", selfcontained = TRUE)


```

```{r, echo = FALSE}
# knitr::opts_chunk$set(echo = TRUE)
# library(dplyr)
# library(tidyr)
# library(plotly)
# 
# data <- read.csv("../../ATLAS Data/ATLAS_space_geo.csv")
# 
# plotly_hist <- function(data) {
#   TaskType_counts <- data %>%
#     separate_rows(DependentMeasurePrimary, sep = "\\+") %>%
#     mutate(DependentMeasurePrimary = trimws(DependentMeasurePrimary)) %>%
#     group_by(DependentMeasurePrimary) %>%
#     summarise(count = n())
# 
#   plot <- plot_ly(data = TaskType_counts, x = ~DependentMeasurePrimary, y = ~count, type = "bar") %>%
#     layout(xaxis = list(title = "Task Type"),
#            yaxis = list(title = "Count"))
# 
#   return(plot)
# }
# 
# taskcount_hist <- plotly_hist(data)
# 
# htmlwidgets::saveWidget(taskcount_hist, "taskcount_hist.html", selfcontained = TRUE)
```


# Sample Size and Language Across the Globe
<iframe src="space.location.plot.html" width="950" height="452" style="margin-bottom: 20px;"></iframe>
# Task Type Count
<iframe src="taskcount_hist.html" width="950" height="452" style="margin-bottom: 20px;"></iframe>
# Preferred FoR Count
<iframe src="FoR_hist.html" width="950" height="452" style="margin-bottom: 20px;"></iframe>
# Test Sites by Continent
<iframe src="continent_hist.html" width="950" height="452" style="margin-bottom: 20px;"></iframe>

